---
title: "E1 Testing"
categories: [Analysis, R, Bayesian]
---

## Analyses Strategy

To assess differences between groups, we used Bayesian Mixed Effects Regression. Analyses were done using @burknerBrmsPackageBayesian2017 and @makowskiBayestestRDescribingEffects2019a. 

## Results

### Testing Phase - No feedback. 

In the first part of the testing phase, participants are tested from each of the velocity bands, and receive no feedback after each throw. 

```{r setup, include=FALSE}
source(here::here("Functions", "packages.R"))
test <- readRDS(here("data/e1_08-04-23.rds")) |> 
  filter(expMode2 == "Test") 
options(brms.backend="cmdstanr",mc.cores=4)

```


```{r}
#| label: Band Deviation
#| tbl-cap: "Deviations from target"
#| layout: [[70, 30],[-5]]
e1_testDistRF2_0 <- brm(dist ~ 0 + (condit * vb) + (0 + vb|id),
                        data=test,file=paste0(here::here("data/model_cache","e1_testDistRF2_0")), 
                        iter=5000,chains=4)
mp1 <- model_parameters(e1_testDistRF2_0,effects="fixed")
p1 <- GetModelStats(e1_testDistRF2_0)

kable(p1,escape=F, booktabs=T) |> column_spec(1:8,width="1.5em") |> 
  kable_styling(full_width = F)

```








## Misc 

{{< include "../Misc/alm_table.qmd" >}}







Here is a footnote reference,[^1] and another.[^2]

[^1]: Here is the footnote.
[^2]: Here's one with multiple blocks. Subsequent paragraphs are
    indented to show that they belong to the previous footnote.
    ```         
    { some.code }
    ```
Here is an inline note.[^3]

[^3]: Inlines notes are easier to write, since you don't have to pick an
    identifier and move down to type the note.


## References

::: {#refs}
:::
